---
title: "Assignment_1"
author: "SIVAREDDY"
date: '2022-03-13'
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(readr)
Online_Retail <- read_csv("Online_Retail.csv")
View(Online_Retail)


```

#Question -1 
#Show the breakdown of the number of transactions by countries i.e. how many transactions are 
in the dataset for each country (consider all records including cancelled transactions). Show this 
in total number and also in percentage. Show only countries accounting for more than 1% of the 
total transactions.

```{r}
country_totaltransaction <- table(Online_Retail$Country)
transaction_percent<- round(100*prop.table(country_totaltransaction))
percentage <- cbind(country_totaltransaction, transaction_percent)
Question1_solution <-subset(percentage, transaction_percent >1)
Question1_solution 
```
#Question -2
#Create  a  new  variable  ‘TransactionValue’  that  is  the  product  of  the  exising  ‘Quantity’  and  
‘UnitPrice’ variables. Add this variable to the dataframe.

Creating new variable 
```{r}
Transactionvalue <- c(Online_Retail$Quantity * Online_Retail$UnitPrice)
Online_Retail$Transactionvalue = Transactionvalue
head(Online_Retail)
```

#Question-3
#Using the newly created variable, TransactionValue, show the breakdown of transaction values 
by countries i.e. how much money in total has been spent each country. Show this in total sum of 
transaction values. Show only countries with total transaction exceeding 130,000 British Pound. 

```{r}
library(dplyr)

Total_Transactionvalue <- sum(Transactionvalue)
data <-summarise(group_by(Online_Retail, Country), Total_Transactionvalue)
Transactionvalue_1 <- filter(data,  Total_Transactionvalue>130000)
Transactionvalue_1

```
#This is an optional question which carries additional marks (golden questions). In this question, 
we are dealing with the InvoiceDate variable. The variable is read as a categorical when you read 
data  from  the  file.  Now  we  need  to  explicitly  instruct  R  to  interpret  this  as  a  Date  variable.  
"POSIXlt" and "POSIXct" are two powerful object classes in R to deal with date and time.

```{r}
Temp=strptime(Online_Retail$InvoiceDate,format='%m/%d/%Y %H:%M',tz='GMT') 
head(Temp)

Online_Retail$New_Invoice_Date <- as.Date(Temp) 

Online_Retail$New_Invoice_Date[20000]- Online_Retail$New_Invoice_Date[10]


Invoice_Day_Week =  weekdays(Online_Retail$New_Invoice_Date) 
Online_Retail$Invoice_Day_Week= Invoice_Day_Week


Online_Retail$New_Invoice_Hour = as.numeric(format(Temp, "%H")) 
New_Invoice_Hour = Online_Retail$New_Invoice_Hour


Online_Retail$New_Invoice_Month = as.numeric(format(Temp, "%m")) 
New_Invoice_Month = Online_Retail$New_Invoice_Month

Online_Retail$New_Invoice_Year = as.numeric(format(Temp, "%y"))
New_Invoice_Year<- Online_Retail$New_Invoice_Year

```


#4a


```{r}
Online_Retail %>% select(Invoice_Day_Week,Quantity) %>% filter( Invoice_Day_Week %in%
c("Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday")) %>% count(Invoice_Day_Week)
```

```{r}
All_Transaction <- length(Online_Retail$Quantity)
All_Transaction

# Sunday percent

Sunday=64375

Sunday_Percentage <- (Sunday/All_Transaction)


## Monday percent

Monday=95111
Monday_Percentage <- Monday/All_Transaction

#Tuesday percent
Tuesday = 101808
Tuesday_Percentage<- Tuesday/All_Transaction

##Wednesday percent
Wednesday = 94565
Wednesday_Percentage <- Wednesday/All_Transaction

#Thursday percent
Thursday = 103857
Thursday_Percentage <- Thursday/All_Transaction

#Friday percent
Friday = 82193
Friday_Percentage <- Friday/All_Transaction

#Saturday Percent 
Saturday = 0
Saturday_Percentage <- Saturday/All_Transaction

data.frame(Sunday_Percentage,Monday_Percentage,Tuesday_Percentage,Wednesday_Percentage,Thursday_Percentage,Friday_Percentage,Saturday_Percentage)

```

#4b
```{r}
Transaction2<- Online_Retail %>% select(Invoice_Day_Week,Quantity) %>%
filter(Invoice_Day_Week=="Sunday")
sum_sunday<- sum(Transaction2$Quantity)
sum_sunday

Transaction2<- Online_Retail %>% select(Invoice_Day_Week,Quantity) %>%
filter(Invoice_Day_Week=="Monday")
sum_monday<- sum(Transaction2$Quantity)
sum_monday

Transaction2<-  Online_Retail %>% select(Invoice_Day_Week,Quantity) %>%
filter(Invoice_Day_Week=="Tuesday")
sum_tuesday<- sum(Transaction2$Quantity)
sum_tuesday

Transaction2<- Online_Retail %>% select(Invoice_Day_Week,Quantity) %>%
filter(Invoice_Day_Week=="Wednesday")
sum_wednesday<- sum(Transaction2$Quantity)
sum_wednesday

Transaction2<- Online_Retail %>% select(Invoice_Day_Week,Quantity) %>%
filter(Invoice_Day_Week=="Thursday")
sum_thursday<- sum(Transaction2$Quantity)
sum_thursday

Transaction2<- Online_Retail %>% select(Invoice_Day_Week,Quantity) %>%
filter(Invoice_Day_Week=="Friday")
sum_friday<- sum(Transaction2$Quantity)
sum_friday

Transaction2<- Online_Retail %>% select(Invoice_Day_Week,Quantity) %>%
filter(Invoice_Day_Week=="Saturday")
sum_saturday<- sum(Transaction2$Quantity)
sum_saturday

data.frame(sum_sunday,sum_monday,sum_tuesday,sum_wednesday,sum_thursday,sum_friday,sum_saturday)


```
#4C

```{r}
Trans_volume<- sum(Online_Retail$Quantity)
Trans_volume

percent_sunday<- sum_sunday/Trans_volume
percent_sunday

percent_monday<- sum_monday/Trans_volume
percent_monday

percent_tuesday<- sum_tuesday/Trans_volume
percent_tuesday

percent_wednesday<- sum_wednesday/Trans_volume
percent_wednesday

percent_thursday<- sum_thursday/Trans_volume
percent_thursday

percent_friday<- sum_thursday/Trans_volume
percent_friday

percentage_saturday<- sum_thursday/Trans_volume

data.frame(percent_sunday,percent_monday,percent_tuesday,percent_wednesday,percent_thursday,percent_friday,percentage_saturday)

```






```{r}
#4d

A <- Online_Retail %>% select(InvoiceDate,Quantity,Transactionvalue,Country) %>% filter(Country == "Australia") %>% count(InvoiceDate)
A


```

```{r}
#4e
library(zoo)

Question_e<-summarise(group_by(Online_Retail,New_Invoice_Hour),Transaction_min=n_distinct(InvoiceNo))
Question_e1<-filter(Question_e,New_Invoice_Hour>=7&New_Invoice_Hour<=20)
Question_e2<-rollapply(Question_e1$Transaction_min,3,sum)
Question_e3<-which.min(Question_e2)
Question_e3
```


#5 Plot the histogram of transaction values from Germany. Use the hist() function to plot. 
```{r}
Germany_1<- c(Online_Retail %>% select(Transactionvalue,Country) %>% filter(Country=="Germany"))
hist(Germany_1$Transactionvalue, col ="Orange")
```

#6 Which customer had the highest number of transactions? Which customer is most valuable (i.e.  highest total sum of transactions)? 

Ans. 

customer having highest number of transactions and High valued Customer before removing NA values
```{r}
customer_highnumber_transaction<- Online_Retail %>% select(CustomerID,Quantity,Transactionvalue) %>%count(CustomerID)
which.max(customer_highnumber_transaction$n)

customer_highnumber_transaction ["4373",]

```
High valued Customer before removing NA values

```{r}
highvalued_customer <- group_by(Online_Retail, CustomerID) %>% summarize(transvalue_customer = sum(Transactionvalue))
which.max(highvalued_customer$transvalue_customer)

highvalued_customer["4373",]
```
customer having highest number of transactions and High valued Customer  after removing NA values

```{r}
customer_highnumber_transaction<- na.omit(Online_Retail %>% select(CustomerID,Quantity,Transactionvalue) %>% count(CustomerID))
which.max(customer_highnumber_transaction$n)

customer_highnumber_transaction ["4043",]
```

High valued Customer after removing NA
```{r}
highvalued_customer <- na.omit (group_by(Online_Retail, CustomerID) %>% summarize(transvalue_customer = sum(Transactionvalue)))
which.max(highvalued_customer$transvalue_customer)

highvalued_customer["1704",]
```


#7 Calculate  the  percentage  of  missing  values  for  each  variable  in  the  dataset  (5  marks). 

```{r}
colMeans(is.na(Online_Retail))
```
#8 What are the number of transactions with missing CustomerID records by countries?

```{r}
Online_Retail %>% select(Country,CustomerID) %>% filter(is.na(Online_Retail$CustomerID)) %>% count(Country)
```

#9 On average, how often the costumers comeback to the website for their next shopping? 

```{r}

```

#10In the retail sector, it is very important to understand the return rate of the goods purchased by 
customers.  In  this  example,  we  can  define  this  quantity,  simply,  as  the  ratio  of  the  number  of 
transactions cancelled (regardless of the transaction value) over the total number of transactions. 
With this definition, what is the return rate for the French customers? (10 marks). Consider the 
cancelled transactions as those where the ‘Quantity’ variable has a negative value. 

```{r}
Retail_table <- filter(Online_Retail,Country=="France") 
totalrow <- nrow(Retail_table)

cancel <- nrow(subset(Retail_table,Transactionvalue<0))
cancel
```

```{r}
notcancel <- totalrow-cancel 
notcancel
```

```{r}
Total_value = (cancel + notcancel)

canceloftotal_retail=(cancel/Total_value)
canceloftotal_retail
```

#11 What is the product that has generated the highest revenue for the retailer? (i.e. item with the 


```{r}
Product <- (group_by(Online_Retail, Description) %>% summarize( Product =
sum(Transactionvalue)))

which.max(Product$Product)

```


```{r}
Product["1128",]
```

#How many unique customers are represented in the dataset? You can use unique() and length() functions.

```{r}
unique_customer<- sapply(Online_Retail, function(Online_Retail) length(unique(Online_Retail)))
unique_customer
```


```{r}
uniquecustomer_ID <- length(unique(Online_Retail$CustomerID))
uniquecustomer_ID
```



 


